Scottish Child Payment Interventions

### 2024-01-17 minos/outcomes/SCP_vis.Rmd
More additions to SCP_vis.Rmd

```{r}
if (batch) {
  print('batch')
  SF12.change.treated.batch(base, int25All, int50All, int75All, int100All)
} else {
  SF12.change.treated.single(base, int25All, int50All, int75All, int100All)
}
```

>>>>

```{r}
if (batch) {
  SF12.change.treated.batch(base, int25All, int50All, int75All, int100All)
} else {
  SF12.change.treated.single(base, int25All, int50All, int75All, int100All)
}
```
